---
title: ' R package `rrtable` '
author: ' Keon-Woong Moon '
date: '`r Sys.time()`'
header-includes:
- \usepackage{multirow}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage[table]{xcolor}
- \usepackage{tabularx,booktabs}
- \usepackage{boxedminipage}
- \usepackage{graphicx}
- \usepackage{rotating}
- \usepackage{longtable}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE ,message=FALSE,warning=FALSE,comment=NA,
          fig.width=9,fig.asp=0.618,fig.align='center',out.width='70%')
```
```{r,echo= TRUE ,message=FALSE}
require(moonBook)
require(ztable)
require(rrtable)
require(ggplot2)
options(ztable.type='latex')
```

### Introduction 

If you are a data scientist or researcher, you will certainly be interested in reproducible research. R package `rrtable` makes it possible to make reports with HTML, LaTex, MS word or MS Powerpoint formats from a table of R codes. 

 


## Package Installation 

You can install R package `rrtable` with the following command. 

```{r echo=TRUE, eval=FALSE }
if(!require(devtools)){ install.packages("devtools") }
devtools::install_github("cardiomoon/rrtable") 
```



## Package Loading 

You can load the `rrtable` package with the following R command. 

```{r echo=TRUE }
require(rrtable) 
```



## Sample Data 

Sample data sampleData3 is included in rrtable package. You can see the sampleData3 by folllowing R command. 

```{r echo=TRUE, eval=TRUE }
str(sampleData3) 
```



### Paragraph 

You can make a paragraph with this data 

```{r landscape=TRUE ,results='asis'}
ztable3(sampleData3) 
```




\newpage

### mytable object 

You can add mytable object with the following R code. 

```{r,results='asis'}
result= mytable(Dx~.,data=acs) 
print(ztable(result,longtable=TRUE),type='latex')
```



### Plot 

You can insert a plot into your document. 

```{r  }
plot(iris) 
```



### ggplot 

You can insert a ggplot into a document 

```{r  }
ggplot(iris,aes(x=Sepal.Length,y=Sepal.Width,color=Species))+ geom_point() 
```



### R code 

You can insert the result of R code. For example, you can insert the result of regression analysis. 

```{r,echo=TRUE}
fit=lm(mpg~wt*hp,data=mtcars)
summary(fit) 
```



### Two ggplots 

You can insert two parallel ggplots with the following code. 

```{r,out.width='50%',fig.align='default',fig.show='hold'}
ggplot(iris,aes(Sepal.Length,Sepal.Width))+geom_point()
ggplot(iris,aes(Sepal.Length,Sepal.Width,colour=Species))+ geom_point()+guides(colour=FALSE) 
```



### Two plots 

You can insert two parallel plots with the following code. 

```{r,out.width='50%',fig.align='default',fig.show='hold'}
hist(rnorm(1000))
plot(1:10) 
```



## HTML Report 

You can get report with HTML format(this file) by following R command. 

```{r echo=TRUE, eval=FALSE }
data2HTML(sampleData3) 
```



