---
title: ' R package `rrtable` '
author: ' Keon-Woong Moon '
date: "`r Sys.time()`"
output: pdf_document
header-includes:
- \usepackage{multirow}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage[table]{xcolor}
- \usepackage{tabularx,booktabs}
- \usepackage{boxedminipage}
- \usepackage{graphicx}
- \usepackage{rotating}
- \usepackage{longtable}
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE ,message=FALSE,warning=FALSE,comment=NA,
          fig.width=9,fig.asp=0.618,fig.align='center',out.width='70%')
```
```{r,echo= FALSE ,message=FALSE}
require(moonBook)
require(xtable)
require(ztable)
require(rrtable)
require(ggplot2)
require(stringr)
options(ztable.type='latex')
```

If you are a data scientist or researcher, you will certainly be interested in reproducible research. R package `rrtable` makes it possible to make reports with HTML, LaTex, MS word or MS Powerpoint formats from a table of R codes.
 



## Package Installation 

You can install R package `rrtable` with the following command. 

```{r echo=TRUE,eval=FALSE }
if(!require(devtools)){ install.packages("devtools") }
devtools::install_github("cardiomoon/rrtable") 
```



## Package Loading 

You can load the `rrtable` package with the following R command. 

```{r echo=TRUE }
require(rrtable) 
```



## Sample Data 

Sample data sampleData3 is included in rrtable package. You can see the sampleData3 by folllowing R command. 

```{r echo=TRUE }
str(sampleData3) 
```



Or you can make a table of this data 

```{r  ,results='asis'}
HTML2latex=function(data){
    seek=c("\\{","\\}","_","~")
    replace=c("\\\\{","\\\\}","\\\\_","\\\\~{}")
    code=data.frame(seek,replace,stringsAsFactors = FALSE)
 
    fnr=function(x){
        
        for(i in 1:nrow(code)){
            x=str_replace_all(x,code$seek[i],code$replace[i])
        }
        x
    }     

    data[]=lapply(data,fnr)
    data
}

ztable2=function(data,...){
    data1=HTML2latex(data)
    print(ztable(data1,...),include.rownames=FALSE,type="latex")
}

data=sampleData3
xtable(data)
#ztable2(data,sidewaystable=TRUE,longtable=TRUE) 
```



